### 2014-03-12 src/methodology.Rnw
update

\begin{figure*}
<<op,fig.width=10, fig.height=5, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
par(las=1,mfrow = c(1, 2),mar=c(2,8,1,1))
o.all <- cbind(projects = rownames(o.dist.all), stack(o.dist.all))
o.all$ind <- clean(o.all$ind)
bcol <- '#2171B5'
#bcol <- 'darkgray'
icol <- '#9ECAE0'
#icol <- 'lightgray'
o.det <- cbind(projects = rownames(o.dist.det), stack(o.dist.det))
o.det$ind <- clean(o.det$ind)
with(o.det,boxplot(values~ind,horizontal=T,border=c(bcol), col=icol, pch='.', axes=F, ylim=c(0,0.6)))
with(o.all,boxplot(values~ind,horizontal=T,border=c('black'), pch='.',main='Original', cex.axis=0.8, ylim=c(0,0.6),add=T))

r.all <- cbind(projects = rownames(r.dist.all), stack(r.dist.all))
r.all$ind <- clean(r.all$ind)
r.det <- cbind(projects = rownames(r.dist.det), stack(r.dist.det))
r.det$ind <- clean(r.det$ind)
with(r.det,boxplot(values~ind,horizontal=T,border=c(bcol), col=icol, pch='.', axes=F,ylim=c(0,0.6)))
with(r.all,boxplot(values~ind,horizontal=T,border=c('black'), pch='.',main='Randoop', cex.axis=0.8,ylim=c(0,0.6),add=T))
@
\caption{The relative contribution of mutation operators in terms of fraction of mutants generated and detected.
The blue shade represent detected mutants, while black represents total mutants.}
\label{fig:op}
\end{figure*}

@@

We ran mutation analysis on this set of projects using
PIT\cite{pitest}. However, since the operators provided by PIT are limited,
we extended PIT to provide newer operators that are similar to operators
provided by other mutation systems. The set of operators that we used
are provided in Table~\ref{tbl:pitop}. A distribution of these operators
in our projects are provided in Figure~\ref{fig:op}, which shows both the
distribution of complete mutants and the relative detection rates of each
mutation operators. In the figure, there are two box-plots corresponding
to each mutation operator on the Y-axis. The black box represents the
relative frequency of the particular mutation operator in the total mutants
\textit{generated}. For example for projects in the randoop set, the
operator \pitnvmc contributed about 23\% of the total number of mutants
produced while \pitrv contributed about 15\%. Similarly, the blue shaded
box-plot represents the relative frequency of particular mutation operator
in the total mutants \textit{detected}. For example, \pitnvmc contribution
in the detected mutants was 34\% while that of \pitrv was 7\%.

@@

We used several different sampling criterias, based on different strategies of sampling, and what happens when the number of mutants selected falls below a threshold.

>>>>

\begin{figure*}
<<op,fig.width=10, fig.height=5, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
par(las=1,mfrow = c(1, 2),mar=c(2,8,1,1))
o.all <- cbind(projects = rownames(o.dist.all), stack(o.dist.all))
o.all$ind <- clean(o.all$ind)
bcol <- '#2171B5'
#bcol <- 'darkgray'
icol <- '#9ECAE0'
#icol <- 'lightgray'
o.det <- cbind(projects = rownames(o.dist.det), stack(o.dist.det))
o.det$ind <- clean(o.det$ind)
with(o.all,boxplot(values~ind,horizontal=T,border=c(bcol), pch='.', axes=F, ylim=c(0,0.6), col=icol ))
with(o.det,boxplot(values~ind,horizontal=T,border=c('black'), pch='.',main='Original', cex.axis=0.8, ylim=c(0,0.6),add=T))

r.all <- cbind(projects = rownames(r.dist.all), stack(r.dist.all))
r.all$ind <- clean(r.all$ind)
r.det <- cbind(projects = rownames(r.dist.det), stack(r.dist.det))
r.det$ind <- clean(r.det$ind)
with(r.all,boxplot(values~ind,horizontal=T,border=c(bcol), pch='.', axes=F,ylim=c(0,0.6),  col=icol))
with(r.det,boxplot(values~ind,horizontal=T,border=c('black'), pch='.',main='Randoop', cex.axis=0.8,ylim=c(0,0.6),add=T))
@
\caption{The relative contribution of mutation operators in terms of fraction of mutants generated and detected.
The blue shade represent detected mutants, while black represents total mutants.}
\label{fig:op}
\end{figure*}

@@

We ran mutation analysis on this set of projects using
PIT\cite{pitest}. However, since the operators provided by PIT are limited,
we extended PIT to provide newer operators that are similar to operators
provided by other mutation systems. The set of operators that we used
are provided in Table~\ref{tbl:pitop}. A distribution of these operators
in our projects are provided in Figure~\ref{fig:op}, which shows both the
distribution of complete mutants and the relative detection rates of each
mutation operators. In the figure, there are two box-plots corresponding
to each mutation operator on the Y-axis. The black box represents the
relative frequency of the particular mutation operator in the total mutants
\textit{generated}. For example for projects in the randoop set, the
operator \pitnvmc contributed about 34\% of the total number of mutants
produced while \pitrv contributed about 7\%. Similarly, the blue shaded
box-plot represents the relative frequency of particular mutation operator
in the total mutants \textit{detected}. For example, \pitnvmc contribution
in the detected mutants was 23\% while that of \pitrv was 15\%.

@@

We used several different sampling criteria, some of which has been suggested in the literature before,
and some which are variants of previously suggested criterias, and some that have not been used before.
